A Low-cost Natural Interaction System based on a Camera Hand-Gestures Recognizer

### 2011-02-07 paper.tex
last changes

The paper is organized as following.
Section 2 presents the study held on gestures
semantics, sources, and taxonomies and include the presentation of the free
icons library created and used.
Section 3 shows the technical details of handling the camera input for gestures recognition.
Section 4 shows the modes where the gestural informations generated are used
with some screenshots of the running application.
Section 5 answers the usability and naturelness question of the use of gestures
specially in an ubiquitous environment.
Finally section 6 discusses the future of the work and the possible integration of
other multimodal modules.

@@

Figure \ref{pipeline} is a description of the pipeline of the modules used to
extract gestural informations. Each part is described in details in the next
subsections.

\png{pipeline}{Pipeline of the work components showing the routing and
transformation of the camera information until getting the gestural informations
ready to use in the scenario}

@@

\section{Gestural informations and Recognition modes}
The output of the video processing is the input of the recognition module,
which is based on the track location on the screen.
Four different modes are defined according to the hand locations. The switch between them is based on the following grammar:
\begin{description}
 \item[The movement mode:] it is activated when two hands are close to each other, so that the user selects between 4 directions. This mode can be used as input for games to select between the directions.
 \item[The multi-touch mode:] where we consider the similarities between 2D gestures in a tactile multi-touch context and gestures in the 3D space. To do so, we consider the hands blobs in a manner similar to that of two finger tips in the input of a multi-touch device. Based on that, we can recognize well known multi-touch gestures, such as Drag, Pinch/Zoom and Rotate with a consideration of a interaction centroid\cite{CentroidGest} but applied in our case.
 \item[The counter mode:] counts the number of fingers in a preselected hand (the left and right hand are automatically discriminated) by counting the peaks in the simplified contour of the blob. This mode can again be used in games for kids.
 \item[The mouse mode:] it is used to control a cursor to select something in an arbitrary place on the screen. With this mode, we only get the input from a sub zone in the screen and map it to the full screen. We use it in a similar way to a computer touchpad.
The user can validate clicks using a tempo on another zone.
\end{description}

>>>>

The paper is organized as following.
Section 2 presents the study held on gestures
semantics, sources, and taxonomies and include the presentation of the free
icons library created and used.
Section 3 shows the technical details of handling the camera input for gestures recognition.
Section 4 shows the modes where the gestural information generated are used
with some screenshots of the running application.
Section 5 answers the usability and naturelness question of the use of gestures
specially in an ubiquitous environment.
Finally section 6 discusses the future of the work and the possible integration of
other multimodal modules.

@@

Figure \ref{pipeline} is a description of the pipeline of the modules used to
extract gestural information. Each part is described in details in the next
subsections.

\png{pipeline}{Pipeline of the work components showing the routing and
transformation of the camera information until getting the gestural information
ready to use in the scenario}

@@

\section{Gestural information and Recognition modes}
The output of the video processing is the input of the recognition module,
which is based on the track location on the screen.
Four different modes are defined according to the hand locations. The switch between them is based on the following grammar:
\begin{description}
 \item[The movement mode:] it is activated when two hands are close to each other, so that the user selects between 4 directions. This mode can be used as input for games to select between the directions.
 \item[The multi-touch mode:] where we consider the similarities between 2D gestures in a tactile multi-touch context and gestures in the 3D space. To do so, we consider the hands blobs in a manner similar to that of two finger tips in the input of a multi-touch device. Based on that, we can recognize well known multi-touch gestures, such as Drag, Pinch/Zoom and Rotate with a consideration of a interaction centroid\cite{CentroidGest} but applied in our case.
 \item[The counter mode:] counts the number of fingers in a preselected hand (the left and right hand are automatically discriminated) by counting the peaks in the simplified contour of the blob. This mode can again be used in games for kids.
 \item[The mouse mode:] it is used to control a cursor to select something in an arbitrary place on the screen. With this mode, we only get the input from a sub zone in the screen and map it to the full screen. We use it in a similar way to a computer touchpad.
The user can validate clicks using a tempo on another zone.
\end{description}
